An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps

### 2020-01-14 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
Melanoma map

XXX Show whole Australia male liver cancer with choropleth and hexagon tile map, and discuss the pros/cons of the result, for understanding the incidence.

```{r liver-geo}
knitr::include_graphics("figures/aus_liver_m.png")
```

```{r liver-hex}
knitr::include_graphics("figures/aus_liver_m_hex.png")
```

## Election results

XXX Code from web site, and a couple of paragraphs of explanation

@@

XXX show how to make an animation, and make a link to a web page where the animation can be viewed

@@

Alternative maps highlight the value of the statistics across the geographic units. Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area. This acknowledges that the amount of residents can be different but recognises that each population area is equally important. The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections. This map algorithm is implemented in the @sugarbag package written for @R.
The \pkg{sugarbag} package creates tesselated hexagon tilegrams. The Australian application preserves the spatial relationships, emphasising capital cities. The hexagon tile map is a visualisation solution that highlights spatial distributions.

>>>>

The Australian Cancer Atlas [@atlas] allows estimates derived from the models of Standardised Incidence Rates and excess deaths to be downloaded. 
Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Rate of melanoma cancer for all persons for each SA2. The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states. The SA2s around Brisbane stand out as more orange and red.
Comparatively, the hexagon tile map display in Figure \ref{fig:melanoma-hex} draws attention to contrast of the blue areas in Sydney and Melbourne and the capital city of Brisbane. In both Sydney and Melbourne, the hexagons that represent the SA2 areas in the inner-city areas have lower than average Incidence Rates.

With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them. The communities in northern Queensland and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticably below average when contrasted with the heaxgons further south.

To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics. The Standardised Incidence Ratios for each geographic unit are joined to the appropriate polygons.

```{r melanoma-geo, fig.cap = "A choropleth map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated Standardised Incidence Rate of Melanoma for all persons, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"                             }
knitr::include_graphics("figures/aus_melanoma_p.png")
```

To create the hexagon tile map display, the same steps are followed as outlined above:

 - Create the set of centroid points
 - Create the hexagon grid points
 - Allocate each centroid to a hexagon grid point

```{r melanoma-hex, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"}
knitr::include_graphics("figures/aus_melanoma_p_hex.png")
```

@@

The \pkg{gganimate} package can be used to make an animation.
It requires connecting the two displays, which can be done using the \code{sf_id} such as the SA2 name.
The animation^[This animation can be viewed at: ] connecting these two displays will highlight the rapid growth of the inner-city areas, and will decrease the large rural areas.

@@

Alternative maps highlight the value of the statistics across the geographic units. Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area. This acknowledges that the amount of residents can be different but recognises that each population area is equally important. The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections. This map algorithm is implemented in the \pkg{sugarbag} @sugarbag package written for \code{R} @R.
The \pkg{sugarbag} package creates tesselated hexagon tilegrams. The Australian application preserves the spatial relationships, emphasising capital cities. The hexagon tile map is a visualisation solution that highlights spatial distributions.

These hexagons equally represent each area. However, the tesselation does not allow the size of the hexagons to represent another variable.
